Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2024-10-21 manuscript_latex/manuscript.tex
Fixed typo.

\caption{Type I error rate as function of the test statistic $\tau_{\text{ecn}}$ for five datasets, with central portion $\kappa=0.80$. The type I error rate is computed from $m_d=10000$ randomly sampled features, These are sampled from asymmetric generalized normal distributions, with and without outliers (Box-Cox and Yeo-Johnson), or normal distributions with outliers (none). The test statistic is computed as the average residual of each feature after (Box-Cox and Yeo-Johnson) robust location- and shift-invariant power transformation, or before (none).}\label{fig:empirical-central-normality-test-appendix}
\end{figure}

>>>>

\caption{Type I error rate as function of the test statistic $\tau_{\text{ecn}}$ for five datasets, with central portion $\kappa=0.80$. The type I error rate is computed from $m_d=10000$ randomly sampled features. These are sampled from asymmetric generalized normal distributions, with and without outliers (Box-Cox and Yeo-Johnson), or normal distributions with outliers (none). The test statistic is computed as the average residual of each feature after (Box-Cox and Yeo-Johnson) robust location- and shift-invariant power transformation, or before (none).}\label{fig:empirical-central-normality-test-appendix}
\end{figure}
